\documentclass{resume} % Use the custom resume.cls style
\usepackage[default]{lato}
\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry} % Document margins
\usepackage{fontawesome5} %LinkedIn logo
\usepackage{setspace}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Andrew Lin} % Your name
\address{Los Angeles, CA} 
\address{\faIcon{linkedin-in} \space \href{https://www.linkedin.com/in/andrew-y-lin/}{andrew-y-lin} \quad \faEnvelope[Regular] \space \href{mailto:lin.andrew.y@gmail.com}{lin.andrew.y@gmail.com} \quad \faMobile* \space 510-789-3466}

\begin{document}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{EXPERIENCE}

\textbf{Product Manager} \hfill Jan 2022 - Present\\
KUBRA \hfill \textit{Remote}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Orchestrated the vision for a cloud-native SaaS platform for processing 10M+ monthly payments, slashing client onboarding time by 97.5\% and reducing time to make a payment by 60\%.
     \item Identified the need for a single pane of glass for observability and spearheaded the adoption of Honeycomb.io, significantly cutting Mean Time To Resolve (MTTR) issues.
     \item Conducted extensive user research and design reviews for a new client-facing UI to manage payments, contributing to a \$14M revenue pipeline.
     \item Established and enforced team and platform standards, resulting in a noticeable improvement in collaboration, decision preservation, and task tracking.
 \end{itemize}
 
\textbf{Technical Product Manager} \hfill Mar 2020 - Dec 2022\\
LegalZoom \hfill \textit{Remote}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Spearheaded the overhaul of the storage system using a 3rd party cloud storage provider that achieved a 99\% reduction in errors and a 90\% decrease in wait time for ~25k monthly customers.
     \item Launched a legal agreement acceptance flow that attained an industry-high 90\% acceptance rate.
     \item Identified the need for unified logins across LegalZoom products and led a team of globally distributed contractors to reduce the number of logins from 6 to 1.
 \end{itemize}

\textbf{Digital Product Manager} \hfill Oct 2018 - Oct 2019\\
Bobit Business Media \hfill \textit{Torrance, CA}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Conceptualized and launched a new B2B magazine website with 1000+ monthly unique visitors and an average visit duration of 12 minutes.    
     \item Migrated 19 B2B magazine websites into responsive layouts, achieving a 12\% growth in monthly visitors.
 \end{itemize}

\textbf{iOS QA Engineer, Search Ads} \hfill Jan 2016 – Nov 2016\\
Apple \hfill \textit{Cupertino, CA}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Successfully delivered Apple Search Ads with iOS 10 launch, used by  61\% of the top 100 grossing apps and generating \$5B in annual advertising revenue.
     \item Coordinated with product, design, and dev teams to develop continuous integration tests in TeamCity, reducing manual testing by 27\%.
 \end{itemize}

\end{rSection}
%----------------------------------------------------------------------------------------
% SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Product Management & Agile Methodology, User Research, Feature Prioritization, Public Speaking, \\
 & Data Analytics, Cost Estimation, Project Management \\
Tech & Cloud Infrastructure, Prompt Engineering, Event-Driven Architecture, \\ 
 & SQL and No-SQL Databases, Microservices, APIs, Kubernetes \\ 
Software \& Coding & Jira, Confluence, Figma, Salesforce, AWS, Docker, Python, HTML/CSS, SQL,\\
 & Google Analytics, Tableau, Google Workspace, Microsoft Office

\end{tabular}

\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf B.S. Electrical Engineering}, \textit{Cum Laude}, UCLA \hfill {2010 - 2014}

\end{rSection}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS AND AWARDS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Certifications and Awards} 
\href{https://www.credly.com/badges/90c12ee8-0188-4d0a-a7a0-7c0fbd13bd91/linked_in_profile}{AWS Certified Cloud Practitioner}, BSA Eagle Scout

\end{rSection}

\end{document}

