\documentclass{resume}
\usepackage[default]{lato}
\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\usepackage{fontawesome5}

\name{Andrew Lin}
\address{Los Angeles, CA \quad \faIcon{linkedin-in} \space \href{https://www.linkedin.com/in/andrew-y-lin/}{andrew-y-lin} \quad \faEnvelope[Regular] \space \href{mailto:lin.andrew.y@gmail.com}{lin.andrew.y@gmail.com} \quad \faMobile* \space 510-789-3466}

\begin{document}

\begin{rSection}{Summary}
Product Manager with 6+ years building API-driven and cloud-native platforms. Experienced in 0–1 product development, developer experience, and AI-enabled workflows. Strong focus on customer discovery and translating complex workflows into scalable, intuitive systems.
\end{rSection}

\begin{rSection}{Experience}

\textbf{Product Manager} \hfill Jan 2022 - Present\\
KUBRA \hfill \textit{Remote}
\begin{itemize}
\itemsep -3pt
\item Built and owned a cloud-native platform enabling enterprise clients to programmatically manage workflows across \$2.5T+ in annual payment document volume.
\item Reduced onboarding time by 97.5\% through scalable system design, automation, and reusable platform components.
\item Established and led UX research practices, driving customer discovery that informed product strategy, feature prioritization, and workflow design.
\item Translated complex customer support operations into structured platform capabilities and improved user-facing experiences.
\end{itemize}

\textbf{Technical Product Manager} \hfill Mar 2020 - Dec 2021\\
LegalZoom \hfill \textit{Remote}
\begin{itemize}
\itemsep -3pt
\item Led modernization of core platform serving \(\sim\)26K customers per quarter, reducing errors by 99\% and processing time by 90\%.
\item Delivered SSO across six products, improving integration and cross-product experience.
\end{itemize}

\textbf{Digital Product Manager} \hfill Oct 2018 - Oct 2019\\
Bobit Business Media \hfill \textit{Torrance, CA}
\begin{itemize}
\itemsep -3pt
\item Built unified SaaS platform replacing manual publishing workflows, improving scalability and usability.
\end{itemize}

\textbf{iOS QA Engineer, Search Ads} \hfill Jan 2016 - Nov 2016\\
Apple \hfill \textit{Cupertino, CA}
\begin{itemize}
\itemsep -3pt
\item Contributed to launch of Apple Search Ads, supporting large-scale advertiser workflows and platform reliability.
\end{itemize}

\end{rSection}

\begin{rSection}{Projects}

\textbf{AR Speedometer for Snap Spectacles} \\
\href{https://github.com/andrewylin/snap-spectacles/tree/main/Speedometer}{github.com/andrewylin/snap-spectacles/tree/main/Speedometer}
\begin{itemize}
\itemsep -3pt
\item Built augmented reality application demonstrating real-time data visualization and interaction design.
\item Used LLM-assisted tools (Cursor, ChatGPT) to rapidly prototype and iterate on product concepts.
\end{itemize}

\end{rSection}

\begin{rSection}{Skills}

\textbf{Product:} API Platforms, Developer Experience, 0–1 Development, Customer Discovery \\
\textbf{Tech:} AWS, REST APIs, Microservices, SQL, NoSQL \\
\textbf{Tools:} Figma, Jira, Looker, ChatGPT, Claude

\end{rSection}

\begin{rSection}{Education}

B.S. Electrical Engineering, UCLA

\end{rSection}

\end{document}
